FTLR proof cases

### 2018-06-24 fully-abstract-comp/ftlr-proof-cases.tex
More of the FTLR proof and other changes.
Sorry about the big commit.

@@

  \item All of the following hold: (includes cap-manipulation cases: move, cca,

@@

      \item (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$,

@@

      \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$,

@@

      \item (cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$,

@@

        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$ and $\Phi_T(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $k = 1$
      \item (move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_S(r_1)$, and
        $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg \isLinear{w_1}
        \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$) and $k = 2$.
      \item (cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' =

@@

      \item (split) $\Phi_T(r_3) = \Phi_S(r_3) =

@@

      \item (split) $\Phi_T(r_3) = \Phi_S(r_3) =

@@

      \item (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$,

@@

      \item (splice) $\Phi_T(r_2) = ((\perm,\linear),\baddr_2,\eaddr_2,\_)$,

@@

      \item (splice) $\Phi_T(r_2) = \Phi_S(r_2) =

@@

      \item (splice) $\Phi_T(r_2) = \Phi_S(r_2) =

@@

  \item All of the following hold: (includes memory-manipulation cases: store,

@@

  \item All of the following hold: (includes memory-manipulation cases: store,

@@

  \item All of the following hold: (includes control-flow manipulation cases:

@@

    Follows from Lemma~\ref{lem:heap-sat-unchanged-future}, the fact the the heap part of the world remains unchanged and $W_{M,\var{heap}}' \future W_{M,\var{heap}}$.
  \end{itemize}
\end{proof}

>>>>

\begin{lemma}[Capability safety doesn't depend on address]
  \label{lem:cap-in-lrv-regardless-of-addr}
  If
  \[
    \npair{((\perm,\lin),\baddr,\eaddr,\aaddr),((\perm,\lin),\baddr,\eaddr,\aaddr)} \in \lrvg{\trust}(W)
  \]
  then
  \[
    \npair{((\perm,\lin),\baddr,\eaddr,\aaddr'),((\perm,\lin),\baddr,\eaddr,\aaddr')} \in \lrvg{\trust}(W)
  \]
\end{lemma}
\begin{proof}
  TODO (Should be trivial)
\end{proof}

\begin{lemma}[Stack capability safety doesn't depend on address]
\label{lem:stkptr-in-lrv-regardless-of-addr}
  If
  \[
    \npair{(((\perm,\lin),\baddr,\eaddr,\aaddr),\stkptr{\perm,\baddr,\eaddr,\aaddr})} \in \lrvg{\trust}(W)
  \]
  then
  \[
    \npair{(((\perm,\lin),\baddr,\eaddr,\aaddr'),\stkptr{\perm,\baddr,\eaddr,\aaddr'})} \in \lrvg{\trust}(W)
  \]
\end{lemma}
\begin{proof}
  TODO (Should be trivial)
\end{proof}

\begin{lemma}[Seal safety doesn't depend on current seal]
  \label{lem:seal-in-lrv-regardless-of-cur-seal}
  If
  \[
    \npair{(\seal{\sigma_\baddr,\sigma_\eaddr,\sigma},\seal{\sigma_\baddr,\sigma_\eaddr,\sigma})} \in \lrvg{\trust}(W)
  \]
  then
  \[
    \npair{(\seal{\sigma_\baddr,\sigma_\eaddr,\sigma'},\seal{\sigma_\baddr,\sigma_\eaddr,\sigma'})} \in \lrvg{\trust}(W)
  \]
\end{lemma}
\begin{proof}
  TODO (Should be trivial)
\end{proof}

\begin{lemma}[Capability safety monotone w.r.t. permission]
  \label{lem:cap-in-lrv-mono-perm}
  If
  \[
    \npair{((\perm,\lin),\baddr,\eaddr,\aaddr),((\perm,\lin),\baddr,\eaddr,\aaddr)} \in \lrvg{\trust}(W)
  \]
  and
  \[
    \perm' \sqsubseteq \perm
  \]
  then
  \[
    \npair{((\perm',\lin),\baddr,\eaddr,\aaddr),((\perm',\lin),\baddr,\eaddr,\aaddr)} \in \lrvg{\trust}(W)
  \]
\end{lemma}
\begin{proof}
  TODO (Should be trivial)
\end{proof}

\begin{lemma}[Stack capability safety monotone w.r.t. permission]
\label{lem:stkptr-in-lrv-mono-perm}
  If
  \[
    \npair{(((\perm,\lin),\baddr,\eaddr,\aaddr),\stkptr{\perm,\baddr,\eaddr,\aaddr})} \in \lrvg{\trust}(W)
  \]
  and
  \[
    \perm' \sqsubseteq \perm
  \]
  then
  \[
    \npair{(((\perm',\lin),\baddr,\eaddr,\aaddr),\stkptr{\perm',\baddr,\eaddr,\aaddr})} \in \lrvg{\trust}(W)
  \]
\end{lemma}
\begin{proof}
  TODO (Should be trivial)
\end{proof}

@@

  \item \label{case:ftlr:move-cca-etc} All of the following hold: (includes cap-manipulation cases: move, cca,

@@

      \item \label{case:ftlr:move-cca-etc:cca-normal} (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$,

@@

      \item \label{case:ftlr:move-cca-etc:cca-stack}(restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$,

@@

      \item \label{case:ftlr:move-cca-etc:cca-seal}(cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$,

@@

        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$ and $\Phi_T(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k = 1$
      \item \label{case:ftlr:move-cca-etc:move}(move) $w_1 = \Phi_S(r_2)$, $w_1' = \Phi_S'(r_2)$, and $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg \isLinear{w_1} \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$) and $r_1 \neq r_2$ and $k = 2$.
      \item \label{case:ftlr:move-cca-etc:move-eq}(move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_S'(r_1)$ and $k = 1$.
      \item \label{case:ftlr:move-cca-etc:cseal}(cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' =

@@

      \item \label{case:ftlr:move-cca-etc:split-normal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =

@@

      \item \label{case:ftlr:move-cca-etc:split-seal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =

@@

      \item \label{case:ftlr:move-cca-etc:split-stack} (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$,

@@

      \item \label{case:ftlr:move-cca-etc:splice-stack}(splice) $\Phi_T(r_2) = ((\perm,\linear),\baddr_2,\eaddr_2,\_)$,

@@

      \item \label{case:ftlr:move-cca-etc:splice-normal}(splice) $\Phi_T(r_2) = \Phi_S(r_2) =

@@

      \item \label{case:ftlr:move-cca-etc:splice-seal} (splice) $\Phi_T(r_2) = \Phi_S(r_2) =

@@

  \item \label{case:ftlr:store-load-mem} All of the following hold: (includes memory-manipulation cases: store,

@@

  \item \label{case:ftlr:store-load-stack} All of the following hold: (includes memory-manipulation cases: store,

@@

  \item \label{case:ftlr:store-load-jump} All of the following hold: (includes control-flow manipulation cases:

@@

    Follows from Lemma~\ref{lem:heap-sat-unchanged-future}, the fact the the heap part of the world remains unchanged and $W_{M,\var{heap}}' \future W_{M,\var{heap}}$.
  \end{itemize}

  Case \ref{case:ftlr:move-cca-etc}:

  First show: if $\lin = \normal$, then
  \[
    \npair[n-1]{(((\rx,\normal),\baddr,\eaddr,\aaddr),((\rx,\normal),\baddr,\eaddr,\aaddr))} \in \lrvg{\trust}(\purePart{W_R})
  \]
  First observe that by Lemma~\ref{lem:purePart-oplus} $\purePart{W_R} = \purePart{W_\pcreg}$.
  Further, by assumption, Lemma~\ref{lem:downwards-closed}, Lemma~\ref{lem:purePart-oplus}, and Lemma~\ref{lem:non-linear-pure}, we have
  \[
    \npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{}(\purePart{W_R})
  \]

  If $\trust = \trusted$, then by assumption we have $[\baddr,\eaddr] \subseteq \ta$ which means that all the conditions for are met for the capability pair to be in the trusted part of the value relation.

  If $\trust = \untrusted$, then we need to show that the capability pair is in the untrusted part of the value relation which means that we need to show:
  \begin{itemize}
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{}(\normal,\purePart{W_R})$

    This follows by assumption, Lemma~\ref{lem:non-linear-pure}, Lemma~\ref{lem:purePart-oplus}, and Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{}(\purePart{W_R})$

    We already showed this.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \execCond{}(\purePart{W_R})$

    To this end let $W' \future \purePart{W_R}$ and $n' < n-1$ and $\aaddr' \in [\baddr',\eaddr']$ be given, and show
    \[
      \npair[n']{(((\rx,\normal),\baddr',\eaddr',\aaddr'),((\rx,\normal),\baddr',\eaddr',\aaddr'))} \in \lre(W')
    \]
    If $[\baddr',\eaddr'] = \emptyset$, then this is trivial, so assume $[\baddr',\eaddr'] \neq \emptyset$.
    Further, for $n'' \leq n'$ assume
    \begin{itemize}
    \item $\npair[n'']{\reg_S',\reg_T'} \in \lrr(W_R')$
    \item $\memSat{\ms_S',\stk',\ms_\stk',\ms_T'}{W_M'}$
    \item $W' \oplus W_R' \oplus W_M'$ is defined
    \end{itemize}
    and show
    \[
      \npair[n'']{\left(
          \begin{array}{l}
          (\ms_S',\reg_S'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')},\stk',\ms_\stk') \\
          (\ms_T',\reg_T'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')})
          \end{array}
         \right)} \in \lro
    \]
    To this end, we want to use the IH which means that we need the following:
    \begin{itemize}
    \item $\trust = \untrusted$ and $\npair[n'']{[\baddr',\eaddr']} \in \readCond{W'}$

      This follows from the readCondition assumption, Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:downwards-closed}, Lemma~\ref{lem:monotonicity}, Lemma~\ref{lem:purePart-oplus}, and Lemma~\ref{lem:non-linear-pure}.
    \item $\npair[n'']{[\baddr',\eaddr']} \in \xReadCond{W'}$

      This follows from what we already showed about the readXCondition,
      Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:downwards-closed}, and Lemma~\ref{lem:monotonicity}
    \item $\npair[n'']{\reg_S',\reg_T'} \in \lrr(W_R')$

      By assumption.
    \item $\memSat{\ms_S',\stk',\ms_\stk',\ms_T'}{W_M'}$

      By assumption.

    \item $W' \oplus W_R' \oplus W_M'$ is defined

      By assumption
    \end{itemize}
  \end{itemize}

  Now show
  \[
    \npair[n-1]{(\Phi_S'.\reg,\Phi_T'.\reg)} \in \lrrg{\trust}(W_R)
  \]
  assuming that neither of the following is the case:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:move} and $\isLinear{w_2}$ and $r_2 = \pcreg$.
  \item Case \ref{case:ftlr:move-cca-etc:cseal} and $\isLinear{\Phi_S(r_1)}$ and $r_1 = \pcreg$.
  \end{itemize}

  By assumption we have
  \[
    \npair[n]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)
  \]
  which gives us $R_R : (\RegName \setminus \{\pcreg\}) \fun World$ such that $W_R = \bigoplus_{r\in \RegName \setminus \{\pcreg\}} R_R(r)$ and for all $r$ in $\RegName \setminus \{\pcreg\}$ we have $\npair[n]{(\Phi_S.\reg(r),\Phi_T.\reg(r))} \in \lrrg{\trust}(R_R(r))$.
  To this end, we need to consider each of cases \ref{case:ftlr:move-cca-etc:cca-normal}-\ref{case:ftlr:move-cca-etc:splice-seal}:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:cca-normal}:

    Pick $R_R$ as the ownership distribution.
    For $r \neq r_1$ it follows by assumption and Lemma~\ref{lem:downwards-closed}.
    For $r = r_1$ it also follows by assumption and Lemma~\ref{lem:downwards-closed}, \ref{lem:cap-in-lrv-regardless-of-addr}, and \ref{lem:cap-in-lrv-mono-perm}.
  \item Case \ref{case:ftlr:move-cca-etc:cca-stack}:

    Pick $R_R$ as the ownership distribution.
    For $r \neq r_1$ it follows by assumption and Lemma~\ref{lem:downwards-closed}.
    For $r = r_1$ it also follows by assumption and Lemma~\ref{lem:downwards-closed}, \ref{lem:stkptr-in-lrv-regardless-of-addr}, and \ref{lem:stkptr-in-lrv-mono-perm}.
  \item Case \ref{case:ftlr:move-cca-etc:cca-seal}:

    Pick $R_R$ as the ownership distribution.
    For $r \neq r_1$ it follows by assumption and Lemma~\ref{lem:downwards-closed}.
    For $r = r_1$ it also follows by assumption and Lemma~\ref{lem:downwards-closed} and \ref{lem:seal-in-lrv-regardless-of-cur-seal}.

  \item Case \ref{case:ftlr:move-cca-etc:move}:

    Pick the ownership distribution based on the linearity of $w_2$: If $\isLinear{w_2}$, then pick
    \[
      R_R'(r) =
      \begin{cases}
        R_R(r_2) \oplus R(r_1) & r = r_1 \\
        \purePart{W_R}         & r = r_2 \\
        R_R(r)                 & \totherwise
      \end{cases}
    \]
    if $\neg \isLinear{w_2}$, then pick
    \[
      R_R'(r) = R_R(r)
    \]

    In the case where $\isLinear{w_2}$, we may assume $r_2 \neq \pcreg$. We need to show (assuming $r_1 \neq \pcreg$)
    \[
      \npair[n-1]{(\Phi_S'(r_1),\Phi_T'(r_1))} \in \lrvg{\trust}(R_R(r_2) \oplus R(r_1))
    \]
    which is 
    \[
      \npair[n-1]{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(R_R(r_2) \oplus R(r_1))
    \]
    this follows by assumption and Lemma~\ref{lem:monotonicity}.

    We also need to show
    \[
      \npair[n-1]{(\Phi_S'(r_2),\Phi_T'(r_2))} \in \lrvg{\trust}(\purePart{W_R})
    \]
    which is trivial as $\Phi_S'(r_2) = \Phi_T'(r_2) = 0$.

    Finally for $r \neq r_1,r_2,\pcreg$ 
    \[
      \npair[n-1]{(\Phi_S'(r),\Phi_T'(r))} \in \lrvg{\trust}(R_R(r))
    \]
    Follows by assumption and Lemma~\ref{lem:downwards-closed}.

    In the case where $\neg \isLinear{w_2}$

    If $r_2 \neq \pcreg$, then for $r \neq r_1$
    \[
      \npair[n-1]{(\Phi_S'(r),\Phi_T'(r))} \in \lrvg{\trust}(R_R(r))
    \]
    Follows by assumption and Lemma~\ref{lem:downwards-closed}.

    For $r \neq r_1,r_2$
    \[
      \npair[n-1]{(\Phi_S'(r_1),\Phi_T'(r_1))} \in \lrvg{\trust}(R_R(r_1))
    \]
    amounts to
    \[
      \npair[n-1]{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(R_R(r_1))
    \]
    By assumption and Lemma~\ref{lem:purePart-oplus} and \ref{lem:non-linear-pure}.

    If $r_2 = \pcreg$, show
    \[
      \npair[n-1]{(\Phi_S(\pcreg),\Phi_T(\pcreg))} \in \lrvg{\trust}(R(r_1))
    \]
    which follows from Lemma~\ref{lem:monotonicity} and \ref{lem:world-fut-purePart} and what we have proven about the pc.
    \lau{remember to change this if we do not manage to prove that the pc is safe.}
  \item Case \ref{case:ftlr:move-cca-etc:move-eq}:

    Follows from Assumption and Lemma~\ref{lem:downwards-closed}.

  \item Case \ref{case:ftlr:move-cca-etc:cseal}:

TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-normal}:

TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-seal}:

TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-stack}:

TODO
  \item Case \ref{case:ftlr:move-cca-etc:splice-stack}:

TODO
  \item Case \ref{case:ftlr:move-cca-etc:splice-normal}:

TODO
  \item Case \label{case:ftlr:move-cca-etc:splice-seal}:

TODO
  \end{itemize}

  By Lemma~\ref{lem:lro-anti-red-gen} it suffices to show
  \[
    \npair[n-1]{\Phi_S',\Phi_T'} \in \lro
  \]
  which follows from the induction hypothesis in the case where $\Phi_S'.\reg(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$.
  In this case, the IH is applicable because we have the following:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S'$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}

    We know one of the following holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
    If the latter is the case, then the result follows by Lemma~\ref{lem:downwards-closed}.

    If the former holds, then it follows from Lemma~\ref{lem:ec-reasonable-antired}.

    \item TODO (the remaining cases)
  \end{itemize}

  It remains to show the case where $\Phi_S'.\reg(\pcreg) \neq ((\rx,\lin),\baddr,\eaddr,\_)$

  We still need to show the following cases:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:move} and $\isLinear{w_2}$ and$r_2 = \pcreg$.
    TODO
  \end{itemize}

  Case \ref{case:ftlr:store-load-mem}

  TODO

  Case \ref{case:ftlr:store-load-stack}

  TODO

  Case \ref{case:ftlr:store-load-jump}

  TODO
\end{proof}
